---
title: "Task 5 - Right Wing Authoritarianism Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
  pdf_document: default
---
# Setup

## Loading libraries
```{r message=FALSE}
library(tidyverse)
library(here)
library(readr)
library(data.table)
```

## Loading in cleaned data
```{r message=FALSE}
rwa <- "clean_data/rwa_clean.csv" %>%
    here() %>%
    read_csv()
```

# Data
## Raw
```{r message=FALSE}
"raw_data/rwa.csv" %>%
    here() %>%
    read_csv() %>% 
    data.table()
```

## Clean data
```{r message=FALSE}
rwa %>% 
    data.table()
```

# Questions

## What's the average RWA score for each gender?

```{r}
rwa %>%
  group_by(gender) %>%
  summarise(mean_rwa = mean(rwa))
```


## What's the average RWA score for left handed people vs. right handed people.

```{r}
rwa %>%
  group_by(hand) %>%
  summarise(mean_rwa = mean(rwa))
```


## What's the average family size for each type of childhood?

```{r}
rwa %>%
  group_by(childhood) %>%
  summarise(mean_family_size = mean(family_size))
```

## What's the average time to take the test for each education level?

```{r}
rwa %>%
  group_by(education) %>%
  summarise(mean_test_time = mean(test_time))
```

## Whats the average RWA score for people aged
- Under 18
- 18 to 25
- 26 to 40
- 41 to 60
- Over 60

```{r}
rwa %>%
  mutate(
    age_group = case_when(
      age < 18 ~ "Under 18",
      age < 26 ~ "18 to 25",
      age < 41 ~ "26 to 40",
      age < 61 ~ "41 to 60",
      age > 60 ~ "Over 60"
    )
  ) %>%
  group_by(age_group) %>%
  summarise(
    mean_rwa = mean(rwa)
  )
```


