For each question where we ask for bird names, give the bird’s common name, scientific name and species abbreviation.

```{r}
library(tidyverse)
```

Which bird had the most individual sightings?

```{r}
full_data %>% 
    count(species_abbreviation) %>% 
    top_n(1)
  
```

Which bird had the highest total count?
```{r}
full_data %>% 
 group_by(species_abbreviation) %>% 
    summarise(sum(count)) %>% 
    top_n(1)
```

Which bird had the highest total count above a latitude of -30?
```{r}
full_data %>% 
    filter(lat > -30) %>% 
 group_by(species_abbreviation) %>% 
    summarise(sum(count)) %>% 
    top_n(1)
```

How many different types of birds were only ever seen in groups of 1?

```{r}


        full_data %>% 
    filter(count < 2)  %>% 
        select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation) %>% 
        distinct() %>% 
    arrange(species_abbreviation) %>% 
    count()

```

How many penguins were seen? (Hint: there are many types of penguin)

```{r}
       full_data %>% 
    filter(str_detect( species_common_name_taxon_age_sex_plumage_phase, "penguin")) %>% 
    summarise(sum(count,na.rm = TRUE))

```

