---
title: "Task 3 - Seabirds Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
  pdf_document: default
---
# Setup

```{r message=FALSE}
library(tidyverse)
library(here)
library(readr)
library(readxl)
library(data.table)
```


## Loading in cleaned data
```{r message=FALSE}
full_data <-
  read_csv(here("clean_data/birds_clean.csv"))
```

# Data
## Raw
```{r message=FALSE}
"raw_data/seabirds.xls" %>%
    here() %>%
    read_excel() %>% 
    data.table()
```

## Clean data
```{r message=FALSE}
full_data %>% 
    data.table()
```

# Questions

## Most spotted
Finding the bird with the most individual sightings

```{r}
highest_individual_sightings <- full_data %>% 
    count(species_abbreviation) %>% 
    top_n(1)

  highest_individual_sightings2 <- left_join(highest_individual_sightings, full_data, by = "species_abbreviation")
  
  highest_individual_sightings2 %>% 
    select(n, species_abbreviation, species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase) %>% 
    head(1)

  
```

## Most common
Finding the bird with the highest total count?
```{r message=FALSE, warning=FALSE}
highest_total_count <- full_data %>% 
 group_by(species_abbreviation) %>% 
    summarise(sum(count)) %>% 
    top_n(1)

  highest_total_count2 <- left_join(highest_total_count, full_data, by = "species_abbreviation")
  
  highest_total_count2 %>% 
    select("sum(count)", species_abbreviation, species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase) %>%
    head(1)
```

## Most common northern bird
Finding bird with the highest total count above a latitude of -30?
```{r message=FALSE}
highest_total_count_above_lat_30 <- full_data %>% 
    filter(lat > -30) %>% 
 group_by(species_abbreviation) %>% 
    summarise(sum(count)) %>% 
    top_n(1)


  highest_total_count_above_lat_30_again <- left_join(highest_total_count_above_lat_30, full_data, by = "species_abbreviation")
  
  highest_total_count_above_lat_30_again %>% 
    select("sum(count)", species_abbreviation, species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase) %>%
    head(1)
```

## Lonely birds
How many different types of birds were only ever seen in groups of 1?

```{r}
full_data %>% 
    filter(count < 2)  %>% 
        select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation) %>%
        distinct() %>% 
    arrange(species_abbreviation) %>% 
    count()
```

## Flying is overrated
How many penguins were seen? (N.B. there are many types of penguin)

```{r}
full_data %>% 
    filter(str_detect( species_common_name_taxon_age_sex_plumage_phase, "penguin")) %>% 
    summarise(sum(count,na.rm = TRUE))
```

