---
title: "Task 3"
output:
  html_document:
    df_print: paged
---

```{r}

# Hurdle: Data file is Excel
# Fix:  Use readxl package

library(readxl)
library(here)


# Hurdle: multiple sheets in source data
# Solution: use re-usable function to read any number of sheets from Excel

read_excel_allsheets <-
    function(filename, tibble = TRUE) {
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets,
                function(X) readxl::read_excel(filename, sheet = X))
    if(!tibble) x <- lapply(x, as.data.frame)
    names(x) <- sheets
    x
}

```

```{r}
# Use function to read any multi-sheet Excel file
raw_data <- read_excel_allsheets((here("raw_data/seabirds.xls")))
```


```{r}

# Hurdle: Need to clean data and names later as required
# Fix: Load dplyr and janitor
library(tidyverse)
library(janitor)
```

```{r}
raw_data

```

raw_data is tibble comprising of four columns:
# $`Ship data by record ID`
# $`Bird data by record ID`
# $`Ship data codes`
# $`Bird data codes`

Thankfully the interesting tables obviously include a primary key!

```{r}

# Hurdle: Lots of distrating data or confusing columns within each table
# Fix: Review raw data and analysis questions; identify useful tables; cull useless columns

clean_ship_names <- clean_names(raw_data$`Ship data by record ID`) %>% 
       select(-sdir, -wdir, -atmp, -aprs, -stmp, -sal, -depth, -time) %>% 
    mutate(date = as.Date(date))


clean_bird_names <- clean_names(raw_data$`Bird data by record ID`) %>% 
    select(-age, -wanplum, -plphase, -sex)

# Hurdle: Bird and ship data are in seperate tables
# Fix: Full join tables as not sure what is useful; make life easier by removing unhelpful columns in previous cleaning step; select non-numeric columns first in preparation for tidying data

full_data <-
    full_join(clean_bird_names, clean_ship_names, by = "record_id") %>% 
    select(record_id,date,species_common_name_taxon_age_sex_plumage_phase:count, lat:long)
```



```{r}
# Hurdle: species columns are unhelpful as they also include plumage and age indicators; also inconsistent approach
# Solution: remove if not needed using grep and begin with simplest column; abbrieviations
```

Age info to remove:
AD= adult
SUBAD = subadult
IMM= immature
JUV = juvenile


Plumage phase info to remove:
1 = all brown
2 = (brown plumage) breaking
3 = white patch on wing
4 = wing patch breaking
5 = white

```{r}

full_data$species_abbreviation <- full_data$species_abbreviation %>% 
    str_replace_all(" PL[1-5]", "") %>% 
    str_replace_all(" AD", "") %>%
    str_replace_all(" IMM", "") %>%
    str_replace_all(" JUV", "") %>%
    str_replace_all(" SUBAD", "")

full_data$species_common_name_taxon_age_sex_plumage_phase <- full_data$species_common_name_taxon_age_sex_plumage_phase %>% 
    str_replace_all(" PL[1-5]", "") %>% 
    str_replace_all(" AD", "") %>%
    str_replace_all(" IMM", "") %>%
    str_replace_all(" JUV", "") %>%
    str_replace_all(" SUBAD", "")
    

full_data$species_scientific_name_taxon_age_sex_plumage_phase <- full_data$species_scientific_name_taxon_age_sex_plumage_phase %>% 
    str_replace_all(" PL[1-5]", "") %>% 
    str_replace_all(" AD", "") %>%
    str_replace_all(" IMM", "") %>%
    str_replace_all(" JUV", "") %>%
    str_replace_all(" SUBAD", "")

full_data
```


```{r}
# Hurdle: Data is not tidy and there is a range of data types
# Fix: Pivot the numeric data in table longer; sort column order again in previous step as required


longer_data <- full_data %>%
    pivot_longer(-record_id:-species_abbreviation,
                 names_to = "info",
                 values_to = "value") %>% 
    view()

```

For each question where we ask for bird names, give the bird’s common name, scientific name and species abbreviation.

```{r}
library(tidyverse)
```

Which bird had the most individual sightings?

```{r}
highest_individual_sightings <- full_data %>% 
    count(species_abbreviation) %>% 
    top_n(1)


  highest_individual_sightings2 <- left_join(highest_individual_sightings, full_data, by = "species_abbreviation")
  
  highest_individual_sightings2 %>% 
    select(n, species_abbreviation, species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase) %>% 
    head(1)

  
```

Which bird had the highest total count?
```{r}
highest_total_count <- full_data %>% 
 group_by(species_abbreviation) %>% 
    summarise(sum(count)) %>% 
    top_n(1)


  highest_total_count2 <- left_join(highest_total_count, full_data, by = "species_abbreviation")
  
  highest_total_count2 %>% 
    select("sum(count)", species_abbreviation, species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase) %>%
    head(1)
```

Which bird had the highest total count above a latitude of -30?
```{r}
highest_total_count_above_lat_30 <- full_data %>% 
    filter(lat > -30) %>% 
 group_by(species_abbreviation) %>% 
    summarise(sum(count)) %>% 
    top_n(1)


  highest_total_count_above_lat_30_again <- left_join(highest_total_count_above_lat_30, full_data, by = "species_abbreviation")
  
  highest_total_count_above_lat_30_again %>% 
    select("sum(count)", species_abbreviation, species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase) %>%
    head(1)
```

How many different types of birds were only ever seen in groups of 1?

```{r}


        full_data %>% 
    filter(count < 2)  %>% 
        select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation) %>% 
        distinct() %>% 
    arrange(species_abbreviation) %>% 
    count()



```

How many penguins were seen? (Hint: there are many types of penguin)

```{r}
       full_data %>% 
    filter(str_detect( species_common_name_taxon_age_sex_plumage_phase, "penguin")) %>% 
    summarise(sum(count,na.rm = TRUE))

```

