---
title: "Task 6 Analysis - Dog Survey"
output: html_document
---

## Loading libraries and cleaned data
```{r}
library(tidyverse)
library(here)
library(readr)

dogs <- read_csv(here("clean_data/dog_survey_clean.csv"))
```

### Question 1
The client only counts a valid email address as those ending in ‘.com’. How many survey results have a valid email address.

```{r}
dogs %>%
  filter(str_detect(email, ".com$")) %>%
      nrow()
```


### Question 2
What’s the average amount spent on dog food for each dog size.

```{r}
dogs %>%
  group_by(dog_size) %>%
    summarize(avg_spent = mean(amount_spent_on_dog_food, na.rm = TRUE))
```

### Question 3
For owners whose surname starts with a letter in the second half of the alphabet (N onwards) what is the average age of their dog?

```{r}
dogs %>%
  mutate(first_name_letter = substr(last_name, 1, 1)) %>%
  filter(first_name_letter >= "N")
```


### Question 4
The ‘dog_age’ column is the age in human years. If the conversion is 1 human year = 6 dog years, then what is the average dog age for each gender?

```{r}
av_hum_age_per_gender <- dogs %>%
  mutate(human_age = dog_age / 6) %>%
  group_by(dog_gender) %>%
  summarize(avg_hum_age = mean(human_age, na.rm = TRUE))

av_hum_age_per_gender
```

### Question 5
Create a plot of results of question 4.

```{r}
av_hum_age_per_gender %>% 
    ggplot() +
    aes(x = dog_gender, y = avg_hum_age) +
    geom_bar(stat = "identity")
```


