---
title: "Task 2 - Cake Recipe Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
  pdf_document: default
---
# Setup

```{r message=FALSE}
library(tidyverse)
library(here)
library(readr)
library(data.table)
```

## Loading in cleaned data

```{r message=FALSE}
# loading in cleaned data
clean_cake_recipe <-
    here("clean_data/cake_recipes.csv") %>% 
    read_csv()
```

# Data
## Raw
```{r message=FALSE}
# Recipes
"raw_data/cake/cake-ingredients-1961.csv" %>%
    here() %>%
    read_csv() %>% 
    data.table()

#  Cake codes
"raw_data/cake/cake_ingredient_code.csv" %>%
    here() %>%
    read_csv() %>% 
    data.table()
```

## Clean data
```{r message=FALSE}
clean_cake_recipe %>% 
    data.table()
```

# Questions

## Cocoa
Finding cake with the most Cocoa

```{r}
clean_cake_recipe %>% 
    filter(ingredient == "Cocoa") %>% 
    top_n(1, value)
    
```

## Sponge cake
Finding number of cups of ingredients used in total for Sponge cake
```{r}
clean_cake_recipe %>% 
    filter(cake == "Sponge", measure == "cup") %>% 
    summarise(total_cups_ingredients = sum(value))
```

## Teaspoon measures
Finding number of ingredients measured in teaspoons
```{r}
clean_cake_recipe %>% 
    filter(measure == "teaspoon") %>% 
    summarise(ingredients_with_tsp = n_distinct(ingredient))
```

## Special cake
Finding cake with most the unique ingredients
```{r}
clean_cake_recipe %>%
  group_by(cake) %>%
  summarise(n_ingredients = n()) %>%
  top_n(1)
```


## Fancy ingredients
Finding ingredients that are only used once
```{r}
clean_cake_recipe %>%
  group_by(ingredient) %>%
  summarise(n_cakes = n()) %>% 
  filter(n_cakes == 1)
```


