---
title: "Task 4 - Candy Data Analysis"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

## Loading libraries and cleaned data
```{r}
library(tidyverse)
library(here)

candy <- read_csv(here("clean_data/candy_clean.csv"),
# specifying data types
col_types = cols(gender = col_character(), country = col_character()))
```

### Question 1
What is the total number of candy ratings given across the three years?

```{r}
candy %>%
# filtering out NAs
  filter(!is.na(rating)) %>%
  nrow()
```

### Question 2
What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?

```{r}
candy %>%
  group_by(going_out) %>%
# Rounding to whole years
  summarise(avg_age = round(mean(age, na.rm = TRUE))) %>%
# Yes first
    arrange(desc(going_out))

```


### Question 3
For each of joy, despair and meh, which candy bar recieved these ratings the most?

```{r}
candy %>%
# Filtering out NAs
  filter(!is.na(rating)) %>%
  group_by(rating, candy) %>%
  summarise(
    count = n()
  ) %>%
  filter(count == max(count))
```

### Question 4
How many people rated Starburst as despair?

```{r}
candy %>%
  filter(candy == "starburst") %>%
  filter(rating == "despair") %>%
  summarise(id_count = n_distinct(person_id))
```


For the next two questions, count despair as -1, joy as +1 and meh as 0.

```{r}
candy <-
  candy %>%
  mutate(rating_numeric = recode(rating,
                                 joy = 1,
                                 despair = -1,
                                 meh = 0))
```

### Question 5
What was the most popular candy bar by this rating system for each gender in the dataset?

```{r}
candy %>%
  group_by(gender, candy) %>%
  summarise(
    avg_rating = mean(rating_numeric, na.rm = TRUE)
  ) %>%
  filter(avg_rating == max(avg_rating))
```

### Question 6
What was the most popular candy bar in each year?

```{r}
candy %>%
  group_by(year, candy) %>%
  summarise(avg_rating = mean(rating_numeric, na.rm = TRUE)) %>%
  filter(avg_rating == max(avg_rating))
```


### Question 7
What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?


```{r}
candy %>%
  mutate(country = if_else(country %in% c("united states",
                                          "canada",
                                          "united kingdom"),
                           country, "other")) %>%
  group_by(country, candy) %>%
  summarise(avg_rating = mean(rating_numeric, na.rm = TRUE)) %>%
  filter(avg_rating == max(avg_rating))
```

