---
title: "R Notebook"
output: html_notebook
---



1.1.2 Analysis questions

```{r}
library(tidyverse)
library(dplyr)

decathlon_tbl <- here("clean_data/clean_data.rds") %>%
    read_rds() %>% 
    view()
```


Who had the longest long jump seen in the data?
```{r}
    filter(decathlon_tbl, event == "long_jump") %>% 
    arrange(
        desc(event_points)
    ) %>% 
    head(1)
```


What was the average 100m time in each competition?
```{r}
decathlon_tbl %>% 
        filter(event == "x100m") %>% 
        group_by(competition) %>% 
        summarise(average_100m_time = mean(event_points))

```

Who had the highest total points across both competitions?
```{r}
decathlon_tbl %>% 
    group_by(competitor) %>%
    summarise(total_points = sum(overall_competition_points)) %>% 
    arrange(desc(total_points)) %>% 
    head(1)
    
```

What was the shot-put scores for the top three competitors in each competition?
```{r}
decathlon_tbl %>% 
    select(-overall_competition_points, -ranking) %>% 
    filter(event == "shot_put")%>% 
    group_by(competition) %>%
    top_n(3, event_points) %>% 
    arrange(desc(event_points))

```

What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?
```{r}
#check
decathlon_tbl %>% 
    filter(event == "x400m")%>%
    group_by(event_points>50, event_points<50) %>% 
    summarise(average_points = mean(overall_competition_points))
```

