---
title: "Task 1 - Decathlon Data Analysis"
output:
  html_document:
    footer: "footer.html"
    # css: "bootstrap.css"
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction

## Dirty dataset
Decathlon data set comes from FactoMineR package and represents two competitions: Decastar and Olympic Games.

## Source
Department of statistics and computer science, Agrocampus Rennes

  
# Setup

## Loading libraries

```{r message=FALSE}

library(readr)
library(here)
library(janitor)
library(tidyverse)
library(data.table)

```

## Loading cleaned data

```{r message=FALSE}

decathlon <-
here("clean_data/clean_data.rds") %>% 
    read_rds()
```

  
# Data
## Raw
```{r message=FALSE}

"raw_data/decathlon.rds" %>% 
    here() %>%
    read_rds() %>% 
    data.table()
```

## Clean data
```{r message=FALSE}
decathlon %>% 
    data.table()
```

  
# Questions

## Long Jump
Finding the longest long jump in the data
```{r}
decathlon %>%
    group_by(event) %>% 
    filter(event == "long_jump",
           event_points == max(event_points)) %>% 
    select(-ranking:-overall_competition_points)
```



## 100m sprint
Finding the average 100m time for each competition
```{r message=FALSE}
decathlon %>% 
        filter(event == "100m_sprint") %>%
    group_by(competition) %>%
        summarise(average_100m_time = round(mean(event_points), 2))
```

## Best all-rounder
Finding the competitor with the highest total points across both competitions
```{r}
decathlon %>% 
    group_by(competitor) %>%
    summarise(total_competition_points = sum(overall_competition_points)) %>% 
    filter(total_competition_points == max(total_competition_points)) %>% 
    head(3)
    
```


## Shot-put
Finding the shot-put scores for the top three competitors in each competition
```{r}

decathlon %>% 
    select(-overall_competition_points, -ranking) %>% 
    filter(event == "shot_put")%>% 
    group_by(competition) %>%
    top_n(3, event_points) %>% 
    arrange(desc(event_points))

```


## 400m sprint
Calculating the average points for competitors who ran the 400m in less than 50 seconds vs. those that ran 400m in more than 50 seconds
```{r}

decathlon %>% 
    filter(event == "400m_sprint")%>%
    group_by(event_points<50) %>% 
    summarise(average_points = round(mean(overall_competition_points))) %>%
  arrange(desc(average_points))
```

